Simulations

### 2020-12-09 Simulations.Rmd
Update Simulations.Rmd

>>>>

```{r}
calcTotalPoints <- function(season){
  totalPoints <- rep(0, 30)
  for (game in 1:length(seasonGames[[1]])){
    totalPoints[season[[2]][game]] = totalPoints[season[[2]][i]] +   season[[7]][game]
    totalPoints[season[[3]][game]] = totalPoints[season[[3]][i]] + season[[8]][game]
  }
  return(totalPoints)
}
```
